Lineage Analysis of CRISPR and shRNA Screens

### 2018-09-17 lineages_18Q3.Rmd
updated rmd

# Wilcoxon tests: Point mutations {.tabset .tabset-fade .tabset-pills}

@@

Filter for point mutations:
```{r}
crispr_data_ptmuts <- filter(crispr_data, Var_Length == 1)
test_ptmuts <- filter(crispr_data_ptmuts, is.na(group_general_lineage_name))
test_ptmuts <- filter(crispr_data_ptmuts, Hugo_Symbol == "KRAS")
```

@@

>>>>

# Wilcoxon tests: Point mutations

@@

Filter for point mutations:
```{r}
crispr_data_ptmuts <- filter(crispr_data, Var_Length == 1 | is.na(Var_Length))
test_ptmuts <- filter(crispr_data_ptmuts, is.na(group_general_lineage_name))
test_ptmuts <- filter(crispr_data_ptmuts, Hugo_Symbol == "KRAS")
```

@@

# Boxplots for paper outline

```{r fig.height=5, fig.width=12}
genes_lvlA <- c("EGFR", "KRAS", "BRAF", "NRAS", "ERBB2", "MET", "ALK", "AKT1", "PDGFRA", "RET")
crispr_ptmuts_lvlA <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA)
crispr_ptmuts_lvlA$Hugo_Symbol <- ordered(crispr_ptmuts_lvlA$Hugo_Symbol, levels = genes_lvlA)
crispr_ptmuts_lvlA_color <- as.character(crispr_ptmuts_lvlA$Color_DeleteriousMissense)
names(crispr_ptmuts_lvlA_color) <- crispr_ptmuts_lvlA$Mutation_Status_DeleteriousMissense

crispr_ptmuts_lvlA_plot <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Hugo_Symbol, y = Score)) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_violin(mapping = aes(fill = Mutation_Status_DeleteriousMissense), alpha = 0.7, position = position_dodge(0.85)) +
  geom_boxplot(mapping = aes(color = Mutation_Status_DeleteriousMissense), position = position_dodge(0.85), width = 0.1) +
  scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
  scale_color_manual(values = c("black", "black")) +
  guides(color = FALSE) +
  theme(legend.direction = "horizontal", legend.justification = c(1, 0), legend.position = c(1, 0), legend.box.margin = margin(c(10, 10, 10, 10))) +
  labs(fill = "Mutation Status", y = "CERES Score", x = "Gene")
crispr_ptmuts_lvlA_plot
# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot.png", crispr_ptmuts_lvlA_plot, width = 12, height = 5, units = "in")
```
